---
title: "Seurat UMAP"
output: html_notebook
---

Lets load in the dataset and appropriate libraries

```{r}
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
Flu.data <- Read10X(data.dir = "Sequencing/NS_meOH/outs/filtered_gene_bc_matrices/human_flu/")
Flu <- CreateSeuratObject(counts = Flu.data, project = "Flu", min.cells = 3, min.features = 200)
Flu
```

Subset to only cells that met our independent thresholds as derived in our python notebook. Add in metadata for positivity regarding IFN and influenza as well as fractional expression.

```{r}
#subset to accepted cells
acceptedCells <- read.csv("Results/acceptedCells.csv")$cell
Flu <- Flu[, colnames(Flu) %in% acceptedCells]


#only pulling IFNB1 as others are negligibly expressed
Flu[["percent.IFN"]] <- PercentageFeatureSet(Flu, features                                          =c('human-flu-IFNB1','human-flu-IL28B','human-flu-IL28A','human-flu-IL28B','human-flu-IL29'))
Flu[["percent.influenza"]] <- PercentageFeatureSet(Flu, features                                          =c('human-flu-PB2','human-flu-PB1','human-flu-PA','human-flu-HA','human-flu-NP',                                             'human-flu-NA', 'human-flu-M-mRNA','human-flu-NS-mRNA'))
IFNpos <-  read.csv("Results/IFN_list.csv")$cell
Flupos <-  read.csv("Results/Flu_list.csv")$cell

Flu[["IFN.positive"]] <- colnames(Flu) %in% IFNpos
Flu[["Flu.positive"]] <- colnames(Flu) %in% Flupos

```

Normalize, find variable features, cluster
```{r}
Flu <- NormalizeData(Flu)
Flu <- FindVariableFeatures(Flu, selection.method = "vst", nfeatures = 2000)
all.genes <- rownames(Flu)
Flu <- ScaleData(Flu, features = all.genes)
Flu <- RunPCA(Flu, features = VariableFeatures(object = Flu))
ElbowPlot(Flu)
Flu <- FindNeighbors(Flu, dims = 1:15)
Flu <- FindClusters(Flu, resolution = 0.04)
ggsave(c("Figures/elbowplot.pdf"), plot=ElbowPlot(Flu), width=6, height=3.6, units="in")
```
Lets go ahead and cluster via UMAP

```{r}
Flu <- RunUMAP(Flu, dims = 1:15)
DimPlot(Flu, reduction = "umap")

ggsave(c("Figures/FirstCluster.pdf"), plot=DimPlot(Flu, reduction = "umap"), width=6, height=3.6, units="in")

```
How do these clusters reflect our binary assignments of flu positive and interferon positive?

```{r}
FeaturePlot(Flu, features = c("percent.influenza", "percent.IFN", "IFN.positive", "Flu.positive"))
ggsave(c("Figures/binaryAssignmentsCluster.pdf"), plot=FeaturePlot(Flu, features = c("percent.influenza", "percent.IFN", "Flu.positive", "IFN.positive")), width=12, height=7.2, units="in")

```



